---
title: "Final_Regressions"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
d = read.csv('Final_241_Data_Shared.csv')
#d = d[d$Guess_the_Cost <= 2000,]
```

```{r}
standard_conf_int_95 = function(regression, n){
  r = coeftest(regression, vcovHC(regression))
  upper_bound = r[n,1] + 1.96* r[n, 2] 
  lower_bound = r[n,1] -1.96* r[n, 2]
  return (c(lower_bound,upper_bound))
}
```

```{r}
summary(d$Guess_the_Cost[d$French_Purchasing_Page == 1]) #French language only
summary(d$Guess_the_Cost[d$German_Purchasing_Page == 1]) #German language only
summary(d$Guess_the_Cost[d$German_Purchasing_Page == 0 & d$French_Purchasing_Page == 0]) #English language only

```

```{r}
#with outliers
r = lm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page, data = d)

coeftest(r, vcovHC(r))

(French_95 = standard_conf_int_95(r,'French_Purchasing_Page'))
(German_95 = standard_conf_int_95(r,'German_Purchasing_Page'))

sd(d$Guess_the_Cost[d$French_Purchasing_Page == 1])
sd(d$Guess_the_Cost[d$German_Purchasing_Page == 1])
sd(d$Guess_the_Cost[d$German_Purchasing_Page == 0 & d$French_Purchasing_Page ==0])
```

```{r}
hist(d$Guess_the_Cost[d$French_Purchasing_Page == 1])
hist(d$Guess_the_Cost[d$German_Purchasing_Page == 1])
hist(d$Guess_the_Cost[d$German_Purchasing_Page == 0 & d$French_Purchasing_Page == 0])
```




```{r}
(French_effect = cohen.d(Guess_the_Cost~French_Purchasing_Page, data = d[d$German_Purchasing_Page != 1,]))

(German_effect = cohen.d(Guess_the_Cost~German_Purchasing_Page, data = d[d$French_Purchasing_Page != 1,]))
```
**Effect size is very small for both French and German effect**

```{r}
pwr.t2n.test(n1 = NROW(d[d$German_Purchasing_Page != 1 & d$French_Purchasing_Page != 1,]), n2 = NROW(d[d$French_Purchasing_Page == 1,]), d = .045, sig.level = .05)

pwr.t2n.test(n1 = NROW(d[d$German_Purchasing_Page != 1 & d$French_Purchasing_Page != 1,]), n2 = NROW(d[d$German_Purchasing_Page == 1,]), d = 0.037, sig.level = .05)


```

**Due to the high variance in our Guess the Price outcome, our power for detecting an effect between French and English language was 9.8%, and our power for detecting an effect between German and English language was 8.22%.**

**Gpower says effect size f is 0.022**

```{r}
pwr.1way(k=3, n=400, f=0.1, alpha=0.05) #Aiming for effect size of 0.1 - Power of 88%

pwr.1way(k=3, n=400, f=0.022, alpha=0.05) #Got effect size of 0.022 - Power of 9.6%
```

```{r}
r = lm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page*US_Origin, data = d)

coeftest(r, vcovHC(r))
```

```{r}
r = lm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page*Long_Description, data = d)

coeftest(r, vcovHC(r))
```
```{r}
French_cb = lm(French_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$German_Purchasing_Page != 1,])

summary(French_cb)

German_cb = lm(German_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$French_Purchasing_Page != 1,])

summary(German_cb)

French_German_cb = lm(French_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$French_Purchasing_Page == 1 | d$German_Purchasing_Page == 1 ,])

summary(French_German_cb)
```

**p-values greater than .05 for all 3 regressions --> Covariate balance check shows that we cannot reject the null hypothesis that our covariates have no predictive power over our treatment variable**

```{r}
r = lm(Purchase_50 ~French_Purchasing_Page + German_Purchasing_Page, data = d)
coeftest(r, vcovHC(r))

```

```{r}
r = lm(Purchase_35 ~French_Purchasing_Page + German_Purchasing_Page, data = d)
coeftest(r, vcovHC(r))
```

```{r}
r = lm(Purchase_20 ~French_Purchasing_Page + German_Purchasing_Page, data = d)
coeftest(r, vcovHC(r))
```
