---
title: "sharad_rml"
author: "Sharad Varadarajan"
date: "August 14, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath("./"))

library(MASS)
library(stargazer)
library(sandwich)
library(lmtest)
library(nnet)

d = read.csv('Second_Launch_Complete.csv')
d = d[1287:NROW(d),] #Only data from the second launch
```

```{r deduping}
library(data.table)
# Cleaning out incomplete responses before treament exposures
d <- d[!is.na(d$Track),]
#summary(d)
# Counting occurances of IP address and Geo-codes
d$geo_code <- paste(d$LocationLatitude, d$LocationLongitude)
d = d[d$Milk_Cost <= 10.00 | (d$geo_code == 'NA NA' & d$Track!= ''),]
dt = data.table(d)
dt[, `freq_geo` := .N, by = geo_code]
dt[, `freq_ip` := .N, by = IPAddress]
#class(as.data.frame(dt))
#dt
## Creatig 2 dedupped dataset, one with complete dedup where we do not allow any duplicates in IP or Geo code, and one where we exclude IP dupes, but allow up to 5 dups per geo code
complete_dedup<- dt[dt$freq_ip==1 & (dt$freq_geo == 1 | (dt$geo_code == 'NA NA' & Track!= ''))]
#nrow(complete_dedup)
five_or_less_dedup <- dt[dt$freq_ip==1 & dt$freq_geo<=5]
#nrow(five_or_less_dedup)
d<-complete_dedup



d$English_as_primary<-d[,.(abs(d$English_as_primary-2))]
d$English_as_primary<-as.factor(d$English_as_primary)
#Male: original, male=1, female=2
d$Male<-d[,.(abs(d$Male-2))]
d$Male<-as.factor(d$Male)
#household income- as factor due to <20k, >100k, and do not answer
d$Household_Income<-as.factor(d$Household_Income)

#Drink Frequency- options are not linear 
d$Drink_Frequency<-factor(d$Drink_Frequency)

#Cab preference
d$Cab_Preference<-d[,.(abs(d$Cab_Preference-2))]

#Purchase Frequency- also not linear
d$Purchase_Frequency<-factor(d$Purchase_Frequency)


d$same_format_origin<-rep(0,length(d$French_Purchasing_Page))
d[French_Purchasing_Page==1 & US_Origin==0,same_format_origin :=1]
d[German_Purchasing_Page==0 & French_Purchasing_Page==0 & US_Origin==1,same_format_origin :=1]
#French layout+french wine
d$French_format_wine<-rep(0,length(d$French_Purchasing_Page))
d[French_Purchasing_Page==1 & US_Origin==0,"French_format_wine" :=1]
#English layout + US wine
d$English_format_wine<-rep(0,length(d$French_Purchasing_Page))
d[German_Purchasing_Page==0 & French_Purchasing_Page==0 & US_Origin==1,"English_format_wine" :=1]


```



#Attrition
```{r} 
OR = function(regr){
  return(exp(coef(regr)))
}

attrit = subset(d, Finished == 0)
sum(attrit$French_Purchasing_Page == 1)
sum(attrit$German_Purchasing_Page == 1)
sum(attrit$French_Purchasing_Page == 0 & attrit$German_Purchasing_Page == 0)

lm_attrit_format = lm(Finished~French_Purchasing_Page + German_Purchasing_Page, d)
lm_attrit_origin = lm(Finished~ US_Origin, d)
lm_attrit_descrip = lm(Finished~Long_Description, d)

## Logistic regression
LR_format <- glm (Finished ~ French_Purchasing_Page + German_Purchasing_Page, data=d, family = binomial)
LR_origin <- glm (Finished ~ US_Origin , data=d, family = binomial)
LR_descrip <- glm (Finished ~ Long_Description, data=d, family = binomial)

stargazer(lm_attrit_format,lm_attrit_origin,lm_attrit_descrip, title="Attrition Regressions-OLS", align=TRUE, type="text")

stargazer(LR_format, LR_origin, LR_descrip, coef = list(OR(LR_format), OR(LR_origin), OR(LR_descrip)), title="Attrition Regressions-Logistic with Odds Ratio", p.auto = FALSE, align=TRUE, type="text")
```


##Covariate Balance Check

**The p-value on the Fstats are insignificant for all covariate balance regression tests, meaning we cannot reject the null hypothesis that all coefficients are equal to 0**
```{r}

d$French_Purchasing_Page = as.numeric(as.character(d$French_Purchasing_Page))
d$German_Purchasing_Page = as.numeric(as.character(d$German_Purchasing_Page))
d$US_Origin = as.numeric(as.character(d$US_Origin))
d$Long_Description = as.numeric(as.character(d$Long_Description))

#French vs English format
French_cb = lm(French_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$German_Purchasing_Page != 1,])

#German vs English format
German_cb = lm(German_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$French_Purchasing_Page != 1,])

#French vs German format
French_German_cb = lm(French_Purchasing_Page ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d[d$French_Purchasing_Page == 1 | d$German_Purchasing_Page == 1 ,])

#US Origin vs French Origin
Origin_cb = lm(US_Origin ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d)

#Long Description vs Short Description
LD_cb = lm(Long_Description ~ Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, data = d)

stargazer(French_cb,German_cb,French_German_cb,LD_cb, Origin_cb, title ="Covariate Balance Regressions", align=TRUE, type="text",font.size= "scriptsize", column.sep.width = "0.5pt")


```

#GUESS THE PRICE

```{r}
d$French_Purchasing_Page<-factor(d$French_Purchasing_Page)
d$German_Purchasing_Page<-factor(d$German_Purchasing_Page)
d$US_Origin <- factor(d$US_Origin)
d$Long_Description <- factor(d$Long_Description)

d$Male = as.character(d$Male)
d$Household_Income = as.character(d$Household_Income)
d$Cab_Preference = as.character(d$Cab_Preference)
d$English_as_primary = as.character(d$English_as_primary)
d$Drink_Frequency = as.character(d$Drink_Frequency)
d$Purchase_Frequency = as.character(d$Purchase_Frequency)

```

#Individual Treatments- RLM regressions with no covariates

**No statistical significance in treatments**
```{r}
rlm.format<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page, d)
rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)


stargazer(rlm.combined,rlm.format,rlm.origin,rlm.description,title="RLM Basic regressions- no covariates", align=TRUE, type="text")
```

#Individual Treatments- RLM regressions with covariates

**No statistical significance in treatments**
```{r}

rlm.cv<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description +  Male + Household_Income + English_as_primary  + Drink_Frequency + Cab_Preference + Purchase_Frequency, d)

rlm.cv1<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + Male + Household_Income + English_as_primary  + Drink_Frequency + Cab_Preference + Purchase_Frequency, d)

rlm.cv2 <- rlm(Guess_the_Cost~ US_Origin + Male + Household_Income + English_as_primary  + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

rlm.cv3 <- rlm(Guess_the_Cost~ Long_Description + Male + Household_Income + English_as_primary  + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

stargazer(rlm.cv, rlm.cv1, rlm.cv2, rlm.cv3, align=TRUE,type="text", title = "RLM Basic regressions- with covariates")
```

#Saturated

**No statistical significance for treatments**
```{r}
d$Track<-factor(d$Track)

rlm.saturated<-rlm(Guess_the_Cost~ Track + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

stargazer(rlm.saturated, align=TRUE,type="text", title = "RLM regressions- saturated")
```

#Track with no covariates
**TrackFrench_English_long  significant at 10% level** --Didnt Replicate for Launch 2
```{r}

rlm.saturated<-lm(Guess_the_Cost~ Track,d)

stargazer(rlm.saturated, align=TRUE,type="text", title = "RLM regressions- track with no covariates")
```


#Full Interactions without covariates

**Statistical Significance at the 10% level for Long Description** - --Didnt Replicate for Launch 2

```{r}
rlm.interactions<-lm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description,d)

stargazer(rlm.interactions, align=TRUE,type="text", title = "RLM regression- with interactions")
```


#Interaction Pairs without covariates

**Statistical Significance at the 5% level for Long Description (regression without language format)** --Didnt Replicate for Launch 2
**Statistical Significance at the 10% level for interaction term Long Description with US Origin (regression without language format)** --Didnt Replicate for Launch 2
**Statistical Significance at the 10% level for German Purchasing Page (regression without origin)** --Didnt Replicate for Launch 2

```{r}
rlm.i1<-lm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin,d)

rlm.i2<-lm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description,d)

rlm.i3<- lm(Guess_the_Cost~ US_Origin + Long_Description + US_Origin * Long_Description, d)

stargazer(rlm.i1, rlm.i2, rlm.i3, align=TRUE,type="text", title = "RLM regression- with interactions")
```

##Interaction Pairs with covariates

**Statistical Significance at the 10% level for Long Description (regression without language format)** --Didnt Replicate for Launch 2
**Statistical Significance at the 10% level for interaction term Long Description with US Origin (regression without language format)** --Didnt Replicate for Launch 2

```{r}
rlm.i1<-lm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,d) 

rlm.i2<-lm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

rlm.i3<- lm(Guess_the_Cost~ US_Origin + Long_Description + US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, d)

stargazer(rlm.i1, rlm.i2, rlm.i3, align=TRUE,type="text", title = "RLM regression- with interactions")
```

#Interactions - Same Format/Origin without covariates
**No statistical significance for treatment**
```{r}
#models
rlm.same<-rlm(Guess_the_Cost ~ same_format_origin, d)
#summary(lm.same)

rlm.same_indiv<-rlm(Guess_the_Cost ~ French_format_wine + English_format_wine, d)

stargazer(rlm.same,rlm.same_indiv,align=TRUE,type="text")
```



#Interactions - Same Format/Origin with covariates
**No statistical significance for treatment**
```{r}
#models
rlm.same<-rlm(Guess_the_Cost ~ same_format_origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency ,d)
#summary(lm.same)

rlm.same_indiv<-rlm(Guess_the_Cost ~ French_format_wine + English_format_wine + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

stargazer(rlm.same,rlm.same_indiv,align=TRUE,type="text")
```


#Fully Saturated
**No statistical significance for treatment**
```{r}
rlm.fully_sat<-rlm(Guess_the_Cost~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,d)

stargazer(rlm.fully_sat, align=TRUE,type="text", title = "RLM regression- with interactions")
```

###PURCHASE LIKELIHOOD - MULTINOMIAL LOGISTIC REGRESSION

**Using multinomial instead of ordinal due to the proportional odds assumption: The proportional odds assumption means that for each term included in the model, the 'slope' estimate between each pair of outcomes across two response levels are assumed to be the same regardless of which partition we consider**

```{r}
d$max_purchase[!is.na(d$Purchase_50)] = "$0"
d[Purchase_50==1,max_purchase:="$50"]
d[Purchase_35==1 & Purchase_50 == 0,max_purchase:="$35"]
d[Purchase_20==1 & Purchase_50 == 0 & Purchase_35 == 0,max_purchase:="$20"]
d$max_purchase = as.factor(d$max_purchase)
d$max = relevel(d$max_purchase, ref = "$0") 


p_val = function(regr){
z <- summary(regr)$coefficients/summary(regr)$standard.errors
return((1 - pnorm(abs(z), 0, 1)) * 2)
}

risk_ratio = function(regr){
z <- summary(regr)$coefficients/summary(regr)$standard.errors
exp(coef(regr))
}

```


```{r}
test = multinom(max~ French_Purchasing_Page + German_Purchasing_Page, data = d)
stargazer(test, type = 'text', coef = list(risk_ratio(test)), p.auto = FALSE)
```

##Trying binary logit models instead

```{r}
#Odds Ratio
OR = function(regr){
  return(exp(coef(regr)))
}
```

##Log Regression Page Format - No covariates
**No statistical significnace**
```{r}
glm.format_50<-glm(Purchase_50~French_Purchasing_Page + German_Purchasing_Page,family = binomial, d)
glm.format_35<-glm(Purchase_35~French_Purchasing_Page + German_Purchasing_Page,family = binomial, d)
glm.format_20<-glm(Purchase_20~French_Purchasing_Page + German_Purchasing_Page, family = binomial,d)


#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.format_50,glm.format_35,glm.format_20, coef = list(OR(glm.format_50), OR(glm.format_35), OR(glm.format_20)), p.auto = FALSE, title="Log Regression Page Format- Risk Ratios with no covariates", align=TRUE, type="text")
```

##Log Regression Origin - No Covariates
**No statistical significance**
```{r}
glm.origin_50<-glm(Purchase_50~ US_Origin,family = binomial, d)
glm.origin_35<-glm(Purchase_35~ US_Origin,family = binomial, d)
glm.origin_20<-glm(Purchase_20~ US_Origin, family = binomial,d)


#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.origin_50,glm.origin_35,glm.origin_20, coef = list(OR(glm.origin_50), OR(glm.origin_35), OR(glm.origin_20)), p.auto = FALSE, title="Log Regression Wine Origin- Risk Ratios with no covariates", align=TRUE, type="text")
```

##Log Regression Description - No covariates
**No statistical significance**
```{r}
glm.desc_50<-glm(Purchase_50~ Long_Description, family = binomial, d)
glm.desc_35<-glm(Purchase_35~ Long_Description, family = binomial, d)
glm.desc_20<-glm(Purchase_20~ Long_Description, family = binomial,d)


#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.desc_50,glm.desc_35,glm.desc_20, coef = list(OR(glm.desc_50), OR(glm.desc_35), OR(glm.desc_20)), p.auto = FALSE, title="Log Regression Wine Description- Risk Ratios with no covariates", align=TRUE, type="text")
```

##Log Regression Page Format - with covariates
**No statistical significnace in treatment**

```{r}
glm.format_50<-glm(Purchase_50~French_Purchasing_Page + German_Purchasing_Page + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.format_35<-glm(Purchase_35~French_Purchasing_Page + German_Purchasing_Page + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.format_20<-glm(Purchase_20~French_Purchasing_Page + German_Purchasing_Page + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial,d)


#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.format_50,glm.format_35,glm.format_20, coef = list(OR(glm.format_50), OR(glm.format_35), OR(glm.format_20)), p.auto = FALSE, title="Log Regression Page Format- Risk Ratios with covariates", align=TRUE, type="text")
```

##Log Regression Origin - with Covariates
**No statistical significance in treatment**
```{r}
glm.origin_50<-glm(Purchase_50~ US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.origin_35<-glm(Purchase_35~ US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.origin_20<-glm(Purchase_20~ US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial,d)




stargazer(glm.origin_50,glm.origin_35,glm.origin_20, coef = list(OR(glm.origin_50), OR(glm.origin_35), OR(glm.origin_20)), p.auto = FALSE, title="Log Regression Wine Origin- Risk Ratios with covariates", align=TRUE, type="text")
```


##Log Regression Description - with covariates
**No statistical significance**
```{r}
glm.desc_50<-glm(Purchase_50~ Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)
glm.desc_35<-glm(Purchase_35~ Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)
glm.desc_20<-glm(Purchase_20~ Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial,d)


#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.desc_50,glm.desc_35,glm.desc_20, coef = list(OR(glm.desc_50), OR(glm.desc_35), OR(glm.desc_20)), p.auto = FALSE, title="Log Regression Wine Description- Risk Ratios with covariates", align=TRUE, type="text")
```

#Combination Treatment - no covariates
**No statistical significance**

```{r}
glm.comb_50<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin,family = binomial, d)
glm.comb_35<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin,family = binomial, d)
glm.comb_20<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin,family = binomial, d)

#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.comb_50,glm.comb_35,glm.comb_20, coef = list(OR(glm.comb_50), OR(glm.comb_35), OR(glm.comb_20)), p.auto = FALSE, title="Log Regression Combined Treatments- Risk Ratios with no covariates", align=TRUE, type="text")

```

#Combination Treatment - with covariates
**No statistical significance**
```{r}
glm.comb_50<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.comb_35<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.comb_20<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)

#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.comb_50,glm.comb_35,glm.comb_20, coef = list(OR(glm.comb_50), OR(glm.comb_35), OR(glm.comb_20)), p.auto = FALSE, title="Log Regression Combined Treatments- Risk Ratios with covariates", align=TRUE, type="text")

```

#Saturated
**No statistical significance for treatments**
```{r}

glm.sat_50<-glm(Purchase_50~ Track + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.sat_35<-glm(Purchase_35~ Track + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.sat_20<-glm(Purchase_20~ Track + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)

#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.sat_50,glm.sat_35,glm.sat_20, coef = list(OR(glm.sat_50), OR(glm.sat_35), OR(glm.sat_20)), p.auto = FALSE, title="Log Regression Saturated- Risk Ratios with  covariates", align=TRUE, type="text")

```


#Track with no covariates 

**TrackEnglish_German_short significant at the 10% level** --Didnt Replicate for Launch 2
```{r}

glm.sat_50<-glm(Purchase_50~ Track,family = binomial, d)
glm.sat_35<-glm(Purchase_35~ Track,family = binomial, d)
glm.sat_20<-glm(Purchase_20~ Track,family = binomial, d)

#rlm.origin<-rlm(Guess_the_Cost~US_Origin,d)
#rlm.description<-rlm(Guess_the_Cost~Long_Description,d)
#rlm.combined<-rlm(Guess_the_Cost~French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description,d)

stargazer(glm.sat_50,glm.sat_35,glm.sat_20, coef = list(OR(glm.sat_50), OR(glm.sat_35), OR(glm.sat_20)), p.auto = FALSE, title="Log Regression Saturated- Risk Ratios with no covariates", align=TRUE, type="text")

```

#Full Interactions without covariates

**German_Purchasing_Page1:US_Origin1 significant at 5% level for $50 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:Long_Description1 significant at 10% level for $35 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:US_Origin1:Long_Description1 significant at 10% level for $50 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:US_Origin1:Long_Description1 significant at 10% level for $35 purchases** --Didnt Replicate for Launch 2
**Long_Description1 significant at 10% level for $35 purchases** -REPLICATED but with an inverse effect to what was seen before
```{r}
glm.interactions_50<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description, family = binomial, d)

glm.interactions_35<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description, family = binomial, d)

glm.interactions_20<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description, family = binomial, d)

stargazer(glm.interactions_50,glm.interactions_35,glm.interactions_20, coef = list(OR(glm.interactions_50), OR(glm.interactions_35), OR(glm.interactions_20)), p.auto = FALSE, title="Log Regression Full Interactions- Risk Ratios with no covariates", align=TRUE, type="text")
```

#Fully Saturated

**German_Purchasing_Page1:US_Origin1 significant at 10% level for $50 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:Long_Description1 significant at 5% level for $35 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:US_Origin1:Long_Description1 significant at 10% level for $50 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1:US_Origin1:Long_Description1 significant at 5% level for $35 purchases** --Didnt Replicate for Launch 2
**German_Purchasing_Page1 significant at 10% level for $35 purchases** --Didnt Replicate for Launch 2
```{r}
glm.interactions_50<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)

glm.interactions_35<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)

glm.interactions_20<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + Long_Description + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + US_Origin * Long_Description + French_Purchasing_Page * US_Origin * Long_Description + German_Purchasing_Page* US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)

stargazer(glm.interactions_50,glm.interactions_35,glm.interactions_20, coef = list(OR(glm.interactions_50), OR(glm.interactions_35), OR(glm.interactions_20)), p.auto = FALSE, title="Log Regression Full Interactions- Risk Ratios with covariates", align=TRUE, type="text")
```

#Interaction Pairs without covariates

##Interaction Origin w Purchasing Page
**No statistically significant findings**

## Interaction Description with Purchasing Page
**Long_Description1 significant at 10% level for $35 purchases** --Didnt Replicate for Launch 2

## Interaction Description with Origin
**No statistically significant findings**


```{r}
glm.i1<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin,family = binomial ,d)
glm.i2<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin, family = binomial, d)
glm.i3<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin, family = binomial ,d)

glm.i4<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description,family = binomial ,d)
glm.i5<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description, family = binomial, d)
glm.i6<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description, family = binomial ,d)

glm.i7<-glm(Purchase_50~ US_Origin + Long_Description + US_Origin * Long_Description,family = binomial ,d)
glm.i8<-glm(Purchase_35~ US_Origin + Long_Description + US_Origin * Long_Description,family = binomial ,d)
glm.i9<-glm(Purchase_20~ US_Origin + Long_Description + US_Origin * Long_Description,family = binomial ,d)


stargazer(glm.i1,glm.i2,glm.i3, coef = list(OR(glm.i1), OR(glm.i2), OR(glm.i3)), p.auto = FALSE, title="Log Regression Interaction Origin w Purchasing Page- Risk Ratios without covariates", align=TRUE, type="text")

stargazer(glm.i4,glm.i5,glm.i6, coef = list(OR(glm.i4), OR(glm.i5), OR(glm.i6)), p.auto = FALSE, title="Log Regression Interaction Description w Purchasing Page- Risk Ratios without covariates", align=TRUE, type="text")

stargazer(glm.i7,glm.i8,glm.i9, coef = list(OR(glm.i7), OR(glm.i8), OR(glm.i9)), p.auto = FALSE, title="Log Regression Interaction Description w Origin- Risk Ratios without covariates", align=TRUE, type="text")

```

#Interaction Pairs with covariates

##Interaction Origin w Purchasing Page
**French_Purchasing_Page1:US_Origin1 significant at 10% level for $20** --Didnt Replicate for Launch 2
**French_Purchasing_Page1 significant at 5% level for $20** --Didnt Replicate for Launch 2

## Interaction Description with Purchasing Page
**No statistically significant findings**

## Interaction Description with Origin
**No statistically significant findings**


```{r}
glm.i1<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial ,d)
glm.i2<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)
glm.i3<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + US_Origin + French_Purchasing_Page * US_Origin + German_Purchasing_Page * US_Origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial ,d)

glm.i4<-glm(Purchase_50~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial ,d)
glm.i5<-glm(Purchase_35~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial, d)
glm.i6<-glm(Purchase_20~ French_Purchasing_Page + German_Purchasing_Page + Long_Description + French_Purchasing_Page * Long_Description + German_Purchasing_Page * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency, family = binomial ,d)

glm.i7<-glm(Purchase_50~ US_Origin + Long_Description + US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial ,d)
glm.i8<-glm(Purchase_35~ US_Origin + Long_Description + US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial ,d)
glm.i9<-glm(Purchase_20~ US_Origin + Long_Description + US_Origin * Long_Description + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial ,d)


stargazer(glm.i1,glm.i2,glm.i3, coef = list(OR(glm.i1), OR(glm.i2), OR(glm.i3)), p.auto = FALSE, title="Log Regression Interaction Origin w Purchasing Page- Risk Ratios with covariates", align=TRUE, type="text")

stargazer(glm.i4,glm.i5,glm.i6, coef = list(OR(glm.i4), OR(glm.i5), OR(glm.i6)), p.auto = FALSE, title="Log Regression Interaction Description w Purchasing Page- Risk Ratios with covariates", align=TRUE, type="text")

stargazer(glm.i7,glm.i8,glm.i9, coef = list(OR(glm.i7), OR(glm.i8), OR(glm.i9)), p.auto = FALSE, title="Log Regression Interaction Description w Origin- Risk Ratios with covariates", align=TRUE, type="text")

```

#Interactions - Same Format/Origin without covariates
**No statistical significance for treatment**
```{r}
#models
glm.same_50<-glm(Purchase_50~ same_format_origin,family = binomial, d)
glm.same_35<-glm(Purchase_35~ same_format_origin,family = binomial, d)
glm.same_20<-glm(Purchase_20~ same_format_origin,family = binomial, d)

glm.same_indiv_50<-glm(Purchase_50~ French_format_wine + English_format_wine,family = binomial, d)
glm.same_indiv_35<-glm(Purchase_35~ French_format_wine + English_format_wine,family = binomial, d)
glm.same_indiv_20<-glm(Purchase_20~ French_format_wine + English_format_wine,family = binomial, d)


stargazer(glm.same_50,glm.same_35,glm.same_20, coef = list(OR(glm.same_50), OR(glm.same_35), OR(glm.same_20)), p.auto = FALSE, title="Log Regression SameFormat/Origin- Risk Ratios with no covariates", align=TRUE, type="text")

stargazer(glm.same_indiv_50,glm.same_indiv_35,glm.same_indiv_20, coef = list(OR(glm.same_indiv_50), OR(glm.same_indiv_35), OR(glm.same_indiv_20)), p.auto = FALSE, title="Log Regression SameFormat/Origin Individual- Risk Ratios with no covariates", align=TRUE, type="text")



```

#Interactions - Same Format/Origin with covariates
**same_format_origin significant at 10% level for $20 purchases** --Didnt Replicate for Launch 2
**French_format_wine significant at 5% level for $20 purchases** -- Replicated but at 10% level

```{r}
#models
glm.same_50<-glm(Purchase_50~ same_format_origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.same_35<-glm(Purchase_35~ same_format_origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.same_20<-glm(Purchase_20~ same_format_origin + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)

glm.same_indiv_50<-glm(Purchase_50~ French_format_wine + English_format_wine + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.same_indiv_35<-glm(Purchase_35~ French_format_wine + English_format_wine + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)
glm.same_indiv_20<-glm(Purchase_20~ French_format_wine + English_format_wine + Male + Household_Income + English_as_primary + Drink_Frequency + Cab_Preference + Purchase_Frequency,family = binomial, d)


stargazer(glm.same_50,glm.same_35,glm.same_20, coef = list(OR(glm.same_50), OR(glm.same_35), OR(glm.same_20)), p.auto = FALSE, title="Log Regression SameFormat/Origin- Risk Ratios with  covariates", align=TRUE, type="text")

stargazer(glm.same_indiv_50,glm.same_indiv_35,glm.same_indiv_20, coef = list(OR(glm.same_indiv_50), OR(glm.same_indiv_35), OR(glm.same_indiv_20)), p.auto = FALSE, title="Log Regression SameFormat/Origin Individual- Risk Ratios with  covariates", align=TRUE, type="text")



```